Irt plot extra

### 2022-03-24 manuscript.Rmd
Top 10 countried map figure removed
Appendix Removed

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: header.tex
header-includes:
  - \usepackage{rotating}
  - \DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
appendix:
  - "appendix-1.Rmd"
mainfont: Arial
---

@@

```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%'}
knitr::include_graphics('Figures/distribution.png', dpi = 300 )
```

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: header.tex
header-includes:
  - \usepackage{rotating}
  - \DeclareDelayedFloatFlavor{sidewaysfigure}{figure}

mainfont: Arial
---

@@
